\resetVars%
\Song{Hey there Delilah}%
\Youtube{www.google.com}%
\Tutorial{www.youtube.com}%
\Author{Plain White T's}%
\makeheader%
\lyrics%

\C{D} Hey there Delilah, \C{F\guitarSharp}what's it like in New York City?
\C{D}I'm a thousand miles away, But girl tonight you look so pretty,
Yes \C{Bm}you do, \C{G}Time Square can't \C{A}shine as bright as \C{Bm}you,
I swear \C{A}it's true.

Hey there Delilah, Don't you worry about the distance,
I'm right there if you get lonely, Give this song another listen,
Close your eyes, Listen to my voice it's my disguise,
I'm by your side.

\C{D}Oh it's what you do to \C{Bm}me, Oh it's what you do to me,
Oh it's what you do to me, Oh it's what you do to me,
What you do to me.

Hey there Delilah, I know times are getting hard,
But just believe me girl some day, I'll pay the bills with this guitar,
We'll have it good, We'll have the life we knew we would,
My word is good.

Hey there Delilah, I've got so much left to say,
If every simple song I wrote to you, Would take your breath away,
I'd write it all, Even more in love with me you'd fall,
We'd have it all.

Oh it's what you do to me, Oh it's what you do to me,
Oh it's what you do to me, Oh it's what you do to me,

\continuechords
\C{G}A thousand miles seems pretty far, \C{A} But they've got planes and trains and cars,
\C{D}I'd walk to you if I had no other \C{Bm}way
\C{G}Our friends would all make fun of us,\C{A}And we'll just laugh along because,
\C{D}We know that none of them have felt this \C{Bm}way,
\C{G}Delilah I can promise you, \C{D}That by the time that we get through,
\C{Bm}The world will never ever be the same, \C{A} And you're to blame.

Hey there Delilah you be good, And don't you miss me,
Two more years and you'll be done with school, And I'll be making history,
Like I do, You'll know it's all because of you,
We can do whatever we want to,
Hey there Delilah here's to you, This one's for you.

Oh it's what you do to me, Oh it's what you do to me,
Oh it's what you do to me, Oh it's what you do to me,
What you do to me.
Ohhh

\next
