\resetVars%
\Song{Listen To Your Heart}%
\Author{Roxette}%
\MakeHeader%
\Lyrics%
\C{Intro 3x:(Bm G A) B G Em}
\C{Bm}I know \C{G}{there}'s something in the \C{A}{wake} of your \C{Bm}{smile}.
I get \C{G}a notion from the \C{A}{look} in your \C{Bm}eyes, yea.
You've built \C{G}a love but that \C{A}{love} falls \C{Bm}{apart}.
Your little piece of heaven\C{G} turns too dark.\C{Em}

Listen to your \C{Bm}{heart}
\C{G}when he's \C{D}calling for \C{A}{you}.
Listen to your \C{Bm}{heart}
\C{G}there's nothing \C{D}{else} you can \C{A}do.
I don't kn\C{D}ow where you're \C{A}{going}
and \C{G}I don't know \C{D}why,
but listen to your \C{Bm}{heart}
\C{G}before \C{A}you tell him goodbye.\C{Bm}

Sometimes you wonder if this fight is worthwhile.
The precious moments are all lost in the tide, yea.
They're swept away and nothing is what is seems,
the feeling of belonging to your dreams.

Listen to your heart
when he's calling for you.
Listen to your heart
there's nothing else you can do.
I don't know where you're going
and I don't know why,
but listen to your heart
before you tell him goodbye.

\Continuechords
\C{E}And there are voices
that want to be heard.
\C{C{\guitarSharp}m}So much to mention
but you can't find the words.
\C{B}The scent of magic,
the \C{A}{beauty} that's been
when love was wilder \C{C\guitarSharp}than the wind.

Listen to your \C{E{\guitarFlat}m}{heart}
\C{B}when he's \C{F{\guitarSharp}}calling for yo\C{C\guitarSharp}u.
Listen to your  \C{E{\guitarFlat}m}{heart}
\C{B}there's nothing \C{F{\guitarSharp}}{else} you can \C{C{\guitarSharp}}do.
I don't kn\C{F{\guitarSharp}}{ow} where you're \C{C{\guitarSharp}}{going}
and \C{B}{I} don't know \C{F{\guitarSharp}}{why},
but listen to your \C{E{\guitarFlat}m}heart
be\C{C{\guitarSharp}}fore you tell him good\C{E{\guitarFlat}m}bye\C{B}.

Listen to your heart, mm-mmmmmm
I don't know where you're going
and I don't know why,
but listen to your heart
before you tell him goodbye.

\C{C{\guitarSharp} E{\guitarFlat}b B C{\guitarSharp} E{\guitarFlat}m B}

\Next
