\song{Robot Pirates}
\autor{Songs To Wear Pants To} 
\lyrics%
Yo ho ho and a bottle of RAM.

\C{Am}Yar matey! Straight outta Davey Jones' locker,
this one goes out to all my fellow robot pirates.
We be bringing it with da skulls and cross\C{Dm}bones. \C{Em}

Throw your antennas in the \C{Am}air and wave them like you just don't compute.
 We are the Robot Pirates.

\C{Am}We have robot functions, but we have pirate duties.
For instance, we're able to reboot, and we search for booty.
We \C{Dm}{wear} eye patches and are \C{Am}{feared} by the masses.
\C{E}"I have a parrot sitting on my titanium chassis."

That's why you'll hear him say, "Polly want a cracker?"
She's powered by a miniature nuclear reactor.
She \C{Dm}{helps} to defend our ship \C{Am}{from} many attackers.
\C{E}"Who's your biggest enemy?" \C{-}Computer hackers!
                    
\C{Am}We are the Robot \C{D}{Pirates.}
We are \C{Am}{made} of \C{G}metal from our \C{Am}{heads} to our \C{G}{privates}.

We are the Robot Pirates.
Robots are good and pirates are good. 
We do all the things that a robot should.
"I talked to him in binary, and he understood!"
We also do the things that a pirate should.
\continuechords
\C{E}"My leg malfunctioned, so I got one made of wood."

\C{Am - Am - E - Am}%
Yes, break it down now. I'm really feeling that beat.
Shake it, shake, shake it. Shake it, shake, shake it. Shake it, shake, shake it. Shake 
like a sword with a dead guy on it.

We are the Robot Pirates.
We are made of metal from our heads to our privates.
We are the Robot Pirates.
Instead of a chest, treasure goes in memory banks.
If you try to shut me down I will make you walk the plank.
I can cut people open and I don't have to try.
And I got a sweet telescope built into my eye.
Oh, I have to indulge when the ladies beckon.
Watch me mop the whole poop deck in eleven seconds.
I can drop the anchor 'cause I know how to work it.

\C{E}We can't touch the water 'cause it makes us short circuit.
\C{Am}We are the Robot Pirates.
\next